Efficient Management of Meta-level Information for RDF

### 2012-05-11 paper-iswc-reification/paper.tex
made the whole thing compile

\documentclass{llncs}
%
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{epsfig}
\usepackage{url}
\usepackage{color}
\usepackage[utf8]{inputenc}
%\usepackage{subfig}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{makeidx} % allows for indexgeneration
%\usepackage{natbib}
\usepackage{amsmath,amsfonts,amssymb}
%\usepackage[top=3.95cm, bottom=4cm, left=4.6cm, right=4.6cm]{geometry}

@@

%\renewcommand{\baselinestretch}{0.98}
\frontmatter          % for the preliminaries
\pagestyle{headings}  % switches on printing of running heads
\mainmatter           % start of the contributions

@@

%\titlerunning{}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Olaf Hartig$^1$, Mike Personick$^2$, Yrjana Rankka$^3$, Bryan Thompson$^2$, Thanh Tran$^4$}

@@

\institute{
$^1$Humboldt University, Berlin, Germany\\
$^2$SYSTAP LLC, Washington, USA\\
$^3$OpenLink Software, Burlington, USA\\
$^4$Institute AIFB, Karlsruhe Institute of Technology, Germany
}

>>>>

\documentclass{llncs}

\usepackage{amsmath,amssymb}
% \usepackage[ruled,vlined]{algorithm2e}
% \usepackage{graphicx}
% \usepackage{subfig}
% \usepackage{epsfig}
% \usepackage{url}
% \usepackage{color}
% \usepackage[utf8]{inputenc}
%\usepackage{subfig}
%\usepackage{algorithm}
%\usepackage{algorithmic}
% \usepackage{makeidx} % allows for indexgeneration
%\usepackage{natbib}
%\usepackage[top=3.95cm, bottom=4cm, left=4.6cm, right=4.6cm]{geometry}

@@

%\renewcommand{\baselinestretch}{0.98}
% \frontmatter          % for the preliminaries
% \pagestyle{headings}  % switches on printing of running heads
% \mainmatter           % start of the contributions

@@

%\titlerunning{}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Olaf Hartig\inst{1} \and Mike Personick\inst{2} \and Yrj{\"a}n{\"a} Rankka\inst{3} \and Bryan Thompson\inst{2} \and Thanh Tran\inst{4}}

@@

\institute{%
Humboldt-Universit{\"a}t zu Berlin, Berlin, Germany\\
\and
SYSTAP LLC, Washington, USA\\
\and
OpenLink Software, Burlington, USA\\
\and
Institute AIFB, Karlsruhe Institute of Technology, Germany
}

### 2012-05-11 paper-iswc-reification/related.tex
made the whole thing compile

\section{Related Work}
Overview of related work and their problems / reasons why not adopted in commercial solutions, e.g. 
Reification
Reification builds a model of a statement:
_:s1 rdf:subject   :SAP .
_:s1 rdf:predicate :bought .
_:s1 rdf:object    :sybase .
_:s1 rdf:type      rdf:Statement .
_:s1 dc:source     reuters:us-sybase .

-	Has a very bad reputation
-	Extremely inefficient 
-	5x the data on disk when you reify statements.
-	Awkward syntax
-	Cognitively challenging to write queries against reified data
-	Rarely used.
Other approaches to be discussed:
-	Bernhard Schueler, Sergej Sizov, Steffen Staab, Duc Thanh Tran: Querying for meta knowledge. WWW 2008:625-634
-	Thanh Tran, Peter Haase, Boris Motik, Bernardo Cuenca Grau, Ian Horrocks: Metalevel Information in Ontology-Based Applications. AAAI 2008:1237-1242
-	Nuno Lopes, Axel Polleres, Umberto Straccia, Antoine Zimmermann: AnQL: SPARQLing Up Annotated RDFS. International Semantic Web Conference 2010:518-533
-	Antoine Zimmermann, Nuno Lopes, Axel Polleres, Umberto Straccia: A general framework for representing, reasoning and querying with annotated Semantic Web data. J. Web Sem. 11: 72-95 (2012)
-	Umberto Straccia, Nuno Lopes, Gergely Lukacsy, Axel Polleres: A General Framework for Representing and Reasoning with Annotated Semantic Web Data. AAAI 2010
-	Jeremy J. Carroll, Christian Bizer, Patrick J. Hayes, Patrick Stickler: Named graphs. J. Web Sem. (WS) 3(4):247-267 (2005)
-	Paula Severi, José Luiz Fiadeiro, David Ekserdjian: Guiding Reification in OWL through Aggregation. Description Logics 2010
-	Nicole Alexander, Siva Ravada: RDF Object Type and Reification in the Database. ICDE 2006:93
Solution & Contributions
-	Efficient management of meta-level statements 
o	Avoids the 5x growth in data associated with RDF Reification
o	Fast query answering
-	Convenient syntax for data and queries
o	Proposed extensions for SPARQL, Turtle
-	Harmonized with RDF Reification
o	Existing data and queries still work
o	Extension to SPARQL Semantics and Algebra
-	Can be combined with named graphs
o	Both methods can be mixed in the same database.

>>>>

\section{Related Work}
Overview of related work and their problems / reasons why not adopted in commercial solutions, e.g. 
Reification
Reification builds a model of a statement:
\_:s1 rdf:subject   :SAP .
\_:s1 rdf:predicate :bought .
\_:s1 rdf:object    :sybase .
\_:s1 rdf:type      rdf:Statement .
\_:s1 dc:source     reuters:us-sybase .

-	Has a very bad reputation
-	Extremely inefficient 
-	5x the data on disk when you reify statements.
-	Awkward syntax
-	Cognitively challenging to write queries against reified data
-	Rarely used.
Other approaches to be discussed:
-	Bernhard Schueler, Sergej Sizov, Steffen Staab, Duc Thanh Tran: Querying for meta knowledge. WWW 2008:625-634
-	Thanh Tran, Peter Haase, Boris Motik, Bernardo Cuenca Grau, Ian Horrocks: Metalevel Information in Ontology-Based Applications. AAAI 2008:1237-1242
-	Nuno Lopes, Axel Polleres, Umberto Straccia, Antoine Zimmermann: AnQL: SPARQLing Up Annotated RDFS. International Semantic Web Conference 2010:518-533
-	Antoine Zimmermann, Nuno Lopes, Axel Polleres, Umberto Straccia: A general framework for representing, reasoning and querying with annotated Semantic Web data. J. Web Sem. 11: 72-95 (2012)
-	Umberto Straccia, Nuno Lopes, Gergely Lukacsy, Axel Polleres: A General Framework for Representing and Reasoning with Annotated Semantic Web Data. AAAI 2010
-	Jeremy J. Carroll, Christian Bizer, Patrick J. Hayes, Patrick Stickler: Named graphs. J. Web Sem. (WS) 3(4):247-267 (2005)
-	Paula Severi, Jos{\'e} Luiz Fiadeiro, David Ekserdjian: Guiding Reification in OWL through Aggregation. Description Logics 2010
-	Nicole Alexander, Siva Ravada: RDF Object Type and Reification in the Database. ICDE 2006:93
Solution \& Contributions
-	Efficient management of meta-level statements 
o	Avoids the 5x growth in data associated with RDF Reification
o	Fast query answering
-	Convenient syntax for data and queries
o	Proposed extensions for SPARQL, Turtle
-	Harmonized with RDF Reification
o	Existing data and queries still work
o	Extension to SPARQL Semantics and Algebra
-	Can be combined with named graphs
o	Both methods can be mixed in the same database.
